Initial environmental impacts of Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-08-16 manu-draft.Rmd
water quality summary table added

data(rstrnpts)

@@

* Table 1 Data collected
* Table 2 Stack/effluent characteristics, load estimates
* Table 3 Tukey multiple comparisons of water quality by week/area, with median/min/max

@@

>>>>

data(rstrnpts)
load(file = here('tables/wqsumtab.RData'))

@@

* Table \@ref(tab:wqsumtab) water quality data collected and summarized
* Table 2 Stack/effluent characteristics, load estimates
* Table 3 Tukey multiple comparisons of water quality by week/area, with median/min/max

@@

```{r wqsumtab}
# table stuff
cap.val <- 'Summary of water quality variables collected from March to July 2021 in response to wastewater discharge from Piney Point. Variables are grouped by major areas interest for evaluating status and trends shown in Figure \\@ref(fig:map)a. Summaries are median, maximum, and minimum values. Total observations (N obs.) and values in rnage, above, or below normal ranges are also shown. Normal ranges are defined as within +/-1 standard deviation of the mean for the month of observation from 2006 to 2021 for values collected at the nearest long-term monitoring site to each sample location.'
tab <- wqsumtab
# table
knitr::kable(tab, booktabs = T, caption = cap.val)
```
